Lhyra: Learned HYbrid Recursive Algorithms

### 2019-05-16 paper/main.tex
figure updates
all figures in paper!

\vspace{0.5cm}
\begin{figure}[!h]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{\textsc{Closest Pair} training curve}
        }{
            \includegraphics[width=5.5cm]{example-image}
        }

        \ffigbox{
            \caption{\textsc{Closest Pair} relative performance}
        }{%
            \includegraphics[width=5.5cm]{example-image}
        }
    \end{floatrow}
\end{figure}

@@

\vspace{0.5cm}
\begin{figure}[!ht]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{Random \textsc{Sorting} training curve}
        }{
            \includegraphics[width=5.5cm]{example-image}
        }

        \ffigbox{
            \caption{Random \textsc{Sorting} relative performance}
        }{%
            \includegraphics[width=5.5cm]{example-image}
        }
    \end{floatrow}
\end{figure}

However, Lhyra can perform even better with interesting and changing data distributions.  Take the following example, where lists are already 50\% sorted.

\vspace{0.5cm}
\begin{figure}[!ht]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{Partially-sorted \textsc{Sorting} training curve}
        }{
            \includegraphics[width=5.5cm]{example-image}
        }

        \ffigbox{
            \caption{Partially-sorted \textsc{Sorting} relative performance}
        }{%
            \includegraphics[width=5.5cm]{example-image}
        }
    \end{floatrow}
\end{figure}

>>>>

\begin{figure}[!h]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{\textsc{Closest Pair} training curve}
        }{
            \includegraphics[width=8cm]{images/training_times_points}
        }

        \ffigbox{
            \caption{\textsc{Closest Pair} relative performance}
        }{%
            \includegraphics[width=8cm]{images/relative_plot_points}
        }
    \end{floatrow}
\end{figure}

@@

\begin{figure}[!ht]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{Random \textsc{Sorting} training curve}
        }{
            \includegraphics[width=8cm]{images/training_times_unsorted_lists}
        }

        \ffigbox{
            \caption{Random \textsc{Sorting} relative performance}
        }{%
            \includegraphics[width=8cm]{images/relative_plot_unsorted_lists}
        }
    \end{floatrow}
\end{figure}

However, Lhyra can perform even better with interesting and changing data distributions.  Take the following example, where lists are 80\% nearly sorted.

\begin{figure}[!ht]
    \centering
    \begin{floatrow}
        \ffigbox{
            \caption{Partially-sorted \textsc{Sorting} training curve}
        }{
            \includegraphics[width=8cm]{images/training_times_mostly_sorted_lists}
        }

        \ffigbox{
            \caption{Partially-sorted \textsc{Sorting} relative performance}
        }{%
            \includegraphics[width=8cm]{images/relative_plot_mostly_sorted_lists}
        }
    \end{floatrow}
\end{figure}
